---
title: "Accuracy comparison at 1 vote per document"
output: 
  html_document: 
    keep_md: yes
---

## Dataset

Reading accuracy levels for different methods from a `tsv` file.

```{r}

filename <- "after-random-votes/seq-around1-first.tsv"

col.names <- c("AC", "NVotes", "RunId", "Method", "Topic", "Accuracy")
col.types <- c("character", "numeric", "factor", "factor", "factor", "numeric")

accuracy <- read.delim(filename, header=FALSE, col.names = col.names, colClasses = col.types)
accuracy$AC <- NULL

head(accuracy)
nrow(accuracy)

```

Look at amount of data available for different topics:

```{r results='asis'}
library(knitr)

topic.rows.sorted <- as.data.frame(sort(table(accuracy$Topic)))
colnames(topic.rows.sorted) <- "Points in dataset"
kable(topic.rows.sorted, format="markdown")

```

Amount of data available for different methods:

```{r results='asis'}

method.rows.sorted <- as.data.frame(sort(table(accuracy$Method)))
colnames(method.rows.sorted) <- "Points in dataset"
kable(method.rows.sorted, format="markdown")

```

Method classes are balanced, safe for testing.

## Computing accuracy

Calculate mean accuracies:

```{r}

means <- aggregate(Accuracy ~ Method + Topic, accuracy, mean)

```

Let us print a star in front of a best method for a topic

```{r results='asis'}

means <- cbind(means, Best="")
means$Best <- as.character(means$Best)
for (i in 1:nrow(means)) {
  current <- means[i, "Accuracy"]
  accuracies.on.this.topic <- means[means$Topic == means[i, "Topic"], "Accuracy"]
  max.accuracy <- max(accuracies.on.this.topic)
  if (current == max.accuracy) {
    means[i, "Best"] <- '*'
  }
}

kable(means, format="markdown")

```

## Results

### Best methods for topics

```{r results='asis'}

best.methods <- means[means$Best == '*', c("Topic", "Method")]

row.names(best.methods) <- NULL
kable(best.methods, format="markdown")

```

### Method totals

```{r}

counts <- table(best.methods$Method)
counts <- counts[counts!=0]
counts <- counts[order(counts, decreasing=TRUE)]
counts

```
